plots for paper

### 2019-09-25 src/plots for paper.Rmd
median plot done

meddf <- data.frame(matrix(ncol = 11, nrow = 49))
colnames(meddf) <- c("depth", mthord)

for (m in 1:length(mthord)){
  mth <- mthord[m]
  mthlst <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  rstk <- stack(mthlst)
  rsum <- summary(rstk, na.rm = TRUE)
  rsum <- rsum["Median", ]
  meddf[mth] <- rsum
  dep <- rstk@names
  write.csv(meddf, paste0("../output/maxent/paper_plots/med_data/median.csv"), row.names = TRUE)
 # write.csv(rsum, paste0("../output/maxent/paper_plots/med_data/median_", mth, ".csv"), row.names = TRUE)
}

medlst <- list.files(paste0("../output/maxent/paper_plots/med_data"), pattern = "^median.*.csv", full.names = TRUE)
tables <- lapply(medlst, read.csv, header = TRUE)
allmed <- do.call(cbind, tables)

>>>>

meddf <- data.frame(matrix(ncol = 3, nrow = 490))
colnames(meddf) <- c("layer", "month", "median")
r <- 1

for (m in 1:length(mthord)){
  mth <- mthord[m]
  mthlst <- list.files(paste0("../output/maxent/predictions/", mth), pattern = "^avg_cloglog.*.asc", full.names = TRUE)
  rstk <- stack(mthlst)
  rsum <- summary(rstk, na.rm = TRUE)
  rsum <- rsum["Median", ]
  for (l in 1:length(rsum)){
    meddf$median[r] <- rsum[l]
    meddf$month[r] <- mth
    meddf$layer[r] <- names(rstk[[l]])
    r <- r+1
  }
}

#rename the layers to be just the depth

meddf$layer <- gsub("avg_cloglog_", "", x = meddf$layer)
meddf <- meddf[order(meddf$layer), ]

write.csv(meddf, paste0("../output/maxent/paper_plots/med_data/median.csv"), row.names = FALSE)
```

```{r}
a <- ggplot(data = meddf) + geom_point(aes(y = layer, x = median, colour = month))
a
```
